---
title: "RWorksheet_Quebral#4a"
author: "Myles Andrei Quebral"
date: "2024-10-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. The table below shows the data about shoe size and height. Create a data frame. a. Describe the data.

```{r}
Shoe_size <- c(6.7,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,7.5,10.5,8.5,12.0,10.5)
Height <- c(66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,64.0,74.5,67.0,71.0,71.0)
Gender <- c("F","F","F","F","M","F","F","F","M","F","M","F","M","M")
Shoe.size <- c(13.0,11.5,8.5,5.0,10.0,6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)
Height2 <- c(77.0,72.0,59.0,62.0,72.0,66.0,64.0,67.0,73.0,69.0,72.0,70.0,69.0,70.0)
Gender2 <- c("M","M","F","F","M","F","F","M","M","F","M","M","M","M")

housedata <- data.frame(Shoe_size,Height,Gender,Shoe.size,Height2,Gender2)
print(housedata)

```
#b. Create a subset by males and females with their corresponding shoe size and height.What its result? Show the R scripts.
```{r}
male_subdata <- subset(housedata , Gender == "M")
male_subdata
female_subdata <- subset(housedata , Gender == "F")
female_subdata
```
#c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.

```{r}
mean_shoesize <- mean(housedata$Shoe_size)
mean_shoesize

mean_height <- mean(housedata$Height)
mean_height

```
#d. Is there a relationship between shoe size and height? Why?


#2. Construct character vector months to a factor with factor() and assign the result tofactor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.

```{r}


months <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August","July","December","August","August","September","November","February",
"April")
factor_months_vector <- factor(months)
factor_months_vector
```
#Then check the summary() of the months_vector and factor_months_vector. | Inter-pret the results of both vectors. Are they both equally useful in this case?
```{r}
summary(months)
```
```{r}
summary(factor_months_vector)
```
#4. Create a vector and factor for the table below.
```{r}
direction <- c("East","West","North")
frequency <- c(1,4,3)
factor_data <- factor(direction, levels = c("East", "West", "North"))
factor_data
```
#5. Enter the data below in Excel with file name = import_march.csv
```{r}
setwd("/cloud/project")
import_march <- read.csv("import_march.csv")
import_march
```
#a. Import the excel file into the Environment Pane using read.table() function. Write the code.
```{r}
setwd("/cloud/project")
read_table <- read.table("import_march.csv", header = TRUE, sep = ",")
read_table
```
#b. View the dataset. Write the R scripts and its result.
```{r}
head(import_march)
```



