---
title: "RWorksheet_Quebral#4c"
author: "Myles Andrei Quebral"
date: "2024-11-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("/cloud/project")
mpgdoc <- read.csv("mpg.csv")
```



#b. Which variables from mpg dataset are categorical?
```{r}
# The manufacturer, model, rans, drv, fl, and class
```

# c. Which are continuous variables?
```{r}
# The display, cty and hwy
```

#2. Which manufacturer has the most models in this data set? Which model has the most variations? Show your answer.
```{r}
manu_cars <- table(mpgdoc$manufacturer)
manu_cars

# The manufacturer that has the most models is dodge with 37 models.
```
```{r}
model_cars <- table(mpgdoc$model)
model_cars

# The model that has the most variations is caravan 2wd with 11 variations.
```
# a. Group the manufacturers and find the unique models. Show your codes and result.
```{r}
library("dplyr")
unique_model <- mpgdoc %>% 
 group_by(manufacturer) %>% 
 summarise(models = n_distinct(model))
unique_model
```

#b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r}
library(ggplot2)
unique_model$manufacturer <- as.factor(unique_model$manufacturer)
unique_model$models <- as.numeric(unique_model$models)

plot(unique_model$manufacturer, unique_model$models,
     type = "p", 
     col = "red",
     main = "Number of Unique Models per Manufacturer",
     xlab = "Manufacturer",
     ylab = "Unique Model Count",
     las = 3) 
ggplot(unique_model, aes(manufacturer, models), y = models) +
  geom_bar(stat = "identity", fill = "magenta", color = "skyblue") +
  labs(title = "Number of Unique Models per Manufacturer", x = "Manufacturer", y = "Unique Model Count") 
 
```
# 2. Same dataset will be used. You are going to show the relationship of the model and the manufacturer. a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?

```{r}
library(ggplot2)
ggplot(unique_model, aes(manufacturer, models), y = models) +
  geom_point( color = "skyblue") 
 
 
# it shows the representation of the data using points 
```
# b. For you, is it useful? If not, how could you modify the data to make it more informative?
```{r}
# It is very useful. but if not, you can improve it by transforming the data, summarizing it, using color for categories and trying interactive tools
```

#3. Plot the model and the year using ggplot(). Use only the top 20 observations. Write the codes and its results.
```{r}
library(ggplot2)
top_20_mpgdoc <- mpgdoc %>%
  arrange(desc(mpg)) %>%  # Replace 'mpg' with the appropriate column for ranking
  head(20)
top_20_mpgdoc
ggplot(top_20_mpgdoc, aes(model,year)) + geom_point()
```
#4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result
```{r}
library(dplyr)
car_counts <- mpgdoc %>%
  group_by(model) %>%        # Group the data by the model
  summarise(count = n()) %>% # Count the number of cars in each model
  arrange(desc(count))       # Arrange the results in descending order

car_counts
```
# a. Plot using geom_bar() using the top 20 observations only. The graphs shoudl have a title, labels and colors. Show code and results.
```{r}
library(ggplot2)
ggplot(car_counts, aes(x = model, y = count)) + 
  geom_bar(stat = "identity", fill = "magenta", color = "skyblue") + 
  labs(title = "Top 20 Observations", x = "Model", y = "Count of Cars")
```
#b. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.
```{r}
library(ggplot2)

ggplot(car_counts, aes(x = model, y = count)) + 
  geom_bar(stat = "identity", fill = "magenta", color = "skyblue") + 
  labs(title = "Top 20 Observations", x = "Model", y = "Count of Cars") +
  coord_flip()
```
#5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic color = engine displacement. Title should be “Relationship between No. of Cylinders and Engine Displacement”. a. How would you describe its relationship? Show the codes and its result.

```{r}
library(ggplot2)
ggplot(mpgdoc, aes(x = displ, y = cyl, color = displ)) + geom_point(size = 3) +  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders (cyl)", 
       y = "Engine Displacement (displ)")
```

#6. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped it with a continuous variable you have identified in #1-c. What is its result? Why it produced such output?

```{r}
library(ggplot2)

ggplot(mpgdoc, aes(x = displ, y = hwy, color = cyl)) + 
  geom_point(size = 3) +  
  labs(title = "Relationship between Engine Displacement and Highway MPG",
       x = "Engine Displacement (displ)", 
       y = "Highway MPG (hwy)")
```
# 6. Import the traffic.csv onto your R environment. a. How many numbers of observation does it have? What are the variables of the traffic dataset the Show your answer.


```{r}
setwd("/cloud/project")
traffic_docs <- read.csv("traffic.csv")
```




```{r}
str(traffic_docs)
# There are 48120 observations and 4 variables named DateTime, Junction, Vehicles, and ID
```
# b. subset the traffic dataset into junctions. What is the R codes and its output?
```{r}
junc_list <- split(traffic_docs, traffic_docs$Junction)


```
# c. Plot each junction in a using geom_line(). Show your solution and output.
```{r}
library(ggplot2)

traffic_docs$DateTime <- as.POSIXct(traffic_docs$DateTime, format = "%Y-%m-%d %H:%M:%S")

# Plot each junction using geom_line() and facet_wrap()
ggplot(traffic_docs, aes(x = DateTime, y = Vehicles)) + 
  geom_line(color = "blue") + 
  labs(title = "Traffic Volume Over Time at Each Junction", 
       x = "DateTime", 
       y = "Number of Vehicles") +
  facet_wrap(~ Junction)  

```
# 7. From alexa_file.xlsx, import it to your environment a. How many observations does alexa_file has? What about the number of columns? Show your solution and answer.

```{r}
setwd("/cloud/project")
alexa_file <- read.csv("alexa.csv")


str(alexa_file)
ncol(alexa_file)
# There are 3150 observations and 5 columns in alexa_file

```
#b. group the variations and get the total of each variations. Use dplyr package. Show solution and answer.
```{r}
print(colnames(alexa_file))

variation_totals <- alexa_file %>%
 group_by(variation) %>% 
  summarise(total = n())
variation_totals
```
# c. Plot the variations using the ggplot() function. What did you observe? Complete the details of the graph. Show solution and answer.c. Plot the variations using the ggplot() function. What did you observe? Complete the details of the graph. Show solution and answer.
```{r}
library(ggplot2)
ggplot(alexa_file, aes(x = date, y = variation)) + 
geom_point() + labs(title = "Variations over Time", x = "Date", y = "Variation", color = "Verified")
```
# d. Plot a geom_line() with the date and the number of verified reviews. Complete the details of the graphs. Show your answer and solution.
```{r}
library(ggplot2)
library(dplyr)

alexa_file$date <- as.Date(alexa_file$date, format = "%d-%b-%y")
review_counts <- alexa_file %>%
  group_by(date) %>%
  summarise(review_count = n())
ggplot(data = review_counts, aes(x = date, y = review_count)) +
  geom_line(color = "blue", size = 1) +
  labs(
    title = "Number of Verified Reviews Over Time",
    x = "Date",
    y = "Number of Verified Reviews"
  ) +
  theme_minimal()
```
#e. Get the relationship of variations and ratings. Which variations got the most highest in rating? Plot a graph to show its relationship. Show your solution and answer.
```{r}
library(dplyr)
library(ggplot2)


variation_ratings <- alexa_file %>%
  group_by(variation) %>%
  summarise(average_rating = mean(rating, na.rm = TRUE)) %>%
  arrange(desc(average_rating))


ggplot(variation_ratings, aes(x = reorder(variation, -average_rating), y = average_rating)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +  # Flip coordinates for better readability
  labs(title = "Average Rating by Product Variation",
       x = "Product Variation",
       y = "Average Rating") +
  theme_minimal()
```


