---
title: "Rworksheet_Quebral_4b"
author: "Myles Andrei Quebral"
date: "2024-10-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Using the for loop, create an R script that will display a 5x5 matrix as shown in Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix. Hint Use abs() function to get the absolute value

```{r}
vectorA <- c(1,2,3,4,5)
matrixA <- matrix(0, nrow = 5, ncol = 5)

for (i in 1:5){
    for (j in 1:5){
        matrixA[i,j] <- abs(i-j)
    }
}

print(matrixA)
```
#2. Print the string "*" using for() function. The output should be the same as shown in Figure
```{r}

n_rows <- 6


for (i in 1:n_rows) {

  row_pattern <- paste(rep("*", i), collapse = " ")
  print(row_pattern)
}

```
#3. Get an input from the user to print the Fibonacci sequence starting from the 1st input up to 500. Use repeat and break statements. Write the R Scripts and its output.

```{r}

start_term <- readline(prompt = "Enter the starting term of the Fibonacci sequence: ")

a <- 0
b <- 1
pos <- 1

repeat {

  fib <- a + b
  
  a <- b
  b <- fib
  
  pos <- pos + 1
  
  if (pos >= start_term) {

    if (fib > 500) {
      break
    }
    print(fib)
  }
}
```
#Import the dataset as shown in Figure 1 you have created previously.
#a. What is the R script for importing an excel or a csv file? Display the first 6 rows of the dataset? Show your codes and its result
```{r}
setwd("/cloud/project/Rworksheet#4b")
excel <- read.csv("Excel.csv")
excel
```
```{r}
excel[1:6,]
```
#b. Create a subset for gender(female and male). How many observations are there in Male? How about in Female? Write the R scripts and its output.
```{r}
male_sub <- subset(excel,Gender=="M")
male_sub
fem_sub <- subset(excel ,Gender == "F")
fem_sub

num_male <- nrow(male_sub)
num_female <- nrow(fem_sub)
num_male
num_female
```
#c. Create a graph for the number of males and females for Household Data. Use plot(),chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and its result.
```{r}

gender_counts <- table(excel$Gender)


barplot(
  gender_counts,
  main = "Number of Males and Females in Household Data",
  xlab = "Gender",
  ylab = "Count",
  col = c("lightblue", "pink"),
  legend.text = c("Female", "Male"),
  args.legend = list(x = "topright")
)
```
#5. The monthly income of Dela Cruz family was spent on the following: Food Electricity Savings Miscellaneous 60 10 5 25 a. Create a piechart that will include labels in percentage.Add some colors and title of the chart. Write the R scripts and show its output.
```{r}
expenses <- c(Food = 60, Electricity = 10, Savings = 5, Miscellaneous = 25)


percent_labels <- paste(names(expenses), round(expenses / sum(expenses) * 100), "%")


pie(
  expenses,
  labels = percent_labels,
  col = c("lightgreen", "skyblue", "lightcoral", "gold"),
  main = "Monthly Expenses of Dela Cruz Family"
)
```
#6. Use the iris dataset.
```{r}
data(iris)


species_counts <- table(iris$Species)


species_percent <- round(species_counts / sum(species_counts) * 100)


colors <- c("lightcoral", "gold", "skyblue")


pie(species_counts, 
    labels = paste(names(species_counts), species_percent, "%"), 
    col = colors, 
    main = "Distribution of Iris Species (Spending Categories)")
```
#a. Check for the structure of the dataset using the str() function. Describe what you have seen in the output.
```{r}
str(iris)
```
#b. Create an R object that will contain the mean of the sepal.length, sepal.width,petal.length,and petal.width. What is the R script and its result?
```{r}
mean <- colMeans(iris[, 1:4])
mean
```
#c. Create a pie chart for the Species distribution. Add title, legends, and colors. Write the R script and its result.
```{r}
data(iris)

species_counts <- table(iris$Species)


species_percent <- round(species_counts / sum(species_counts) * 100)


colors <- c("lightcoral", "gold", "skyblue")


pie(species_counts, 
    labels = paste(names(species_counts), species_percent, "%"), 
    col = colors, 
    main = "Distribution of Iris Species (Spending Categories)")
    legend("topright", legend = names(species_counts), fill = colors)
```
#d. Subset the species into setosa, versicolor, and virginica. Write the R scripts and show the last six (6) rows of each species.
```{r}
setosa <- subset(iris, Species == "setosa")
versicolor <- subset(iris, Species == "versicolor")
virginica <- subset(iris, Species == "virginica")

# Display the last six rows of each species
tail(setosa)
tail(versicolor)
tail(virginica)
```
```{r}

iris$Species <- as.factor(iris$Species)

colors <- c("red", "green", "blue")
symbols <- c(16, 17, 18)  


plot(iris$Sepal.Length, iris$Sepal.Width,
     col = colors[iris$Species],        # Colors based on species
     pch = symbols[iris$Species],       # Symbols based on species
     xlab = "Sepal Length",             # Label for x-axis
     ylab = "Sepal Width",              # Label for y-axis
     main = "Iris Dataset",             # Title
     sub = "Sepal Width and Length")    # Subtitle


legend("topright", legend = levels(iris$Species), 
       col = colors, pch = symbols, 
       title = "Species")
```
#f. Interpret the result
# This scatterplot will show the Sepal.Length on the x-axis and Sepal.Width on the y-axis, with points colored and symbolized according to species

# 7. Import the alexa-file.xlsx. Check on the variations. Notice that there are extra whitespaces among black variants (Black Dot, Black Plus, Black Show, BlackSpot). Also on the white variants (White Dot, White Plus, White Show, White Spot).
#a. Rename the white and black variants by using gsub() function.

```{r alexa}
alexa_docs <- read.csv("alexa.csv")

```


```{r}
library(dplyr)
alexa_data <- alexa_docs %>%
  mutate(variation = gsub("Black ", "Green", variation),
         variation = gsub("White ", "Blue", variation))


```
#b. Get the total number of each variations and save it into another object. Save the object as variations.RData. Write the R scripts. What is its result?
```{r}
library(dplyr)
variation_count <- alexa_data %>% count(alexa_data$variation )
save(variation_count, file = "variations.RData")
variation_count
```
#c. From the variations.RData, create a barplot(). Complete the details of the chart which include the title, color, labels of each bar.
```{r}
load("variations.RData")
barplot(height = variation_count$n, 
        names.arg = variation_count$variation,   col = "skyblue",  
        main = "Total Counts of Variations",  
        xlab = "Variations", 
        ylab = "Count",)
```
# d. Create a barplot() for the black and white variations. Plot it in 1 frame, side by side. Complete the details of the chart.

```{r}
black_variations <- alexa_data[grep("Black", alexa_data$variation, ignore.case = TRUE), ]
white_variations <- alexa_data[grep("White", alexa_data$variation, ignore.case = TRUE), ]

# Count the number of reviews for each variation
black_counts <- table(black_variations$variation)
white_counts <- table(white_variations$variation)

par(mfrow = c(1, 2))

# Plot for black variations
barplot(black_counts, main = "Black Variations", col = "black",
        xlab = "Variation", ylab = "Count", las = 1)

# Plot for white variations
barplot(white_counts, main = "White Variations", col = "white",
        xlab = "Variation", ylab = "Count", las = 1)
```



