---
title: "RWorksheet_Quebral#3.rmd"
author: "Myles Andrei Quebral"
date: "2024-09-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. There is a built-in vector LETTERS contains the uppercase letters of the alphabetand letters which contains the lowercase letters of the alphabet.

# Based on the above vector LETTERS:
# a. You need to produce a vector that contains the first 11 letters.
```{r}
Letters <- c("A","B","C","D","E","F","G","H","I","J","K","L","M","N", "O","P","Q","R","S","T","U","V","W","X","Y","Z")

letters <- c("a","b","c","d","e","f","g","h","i","j","k","l","m","n", "o","p","q","r","s","t","u","v","w","x","y","z")
```

```{r}
eleven <- Letters[1:11]
eleven
```

#b. Produce a vector that contains the odd numbered letters.
```{r}
odd <- Letters[seq("1","26", by = 2)]
odd
```

#c. Produce a vector that contains the vowels
```{r}
vowels <- Letters[c(1,5,9,15,21)]
vowels
```
#d. Produce a vector that contains the last 5 lowercase letters.
```{r}
last5 <- tail(letters,5)
last5
```
#e. Produce a vector that contains letters between 15 to 24 letters in lowercase.
```{r}
between <- letters[c(15:24)]
between
```
#2. Create a vector(not a dataframe) with the average temperatures in April for Tugue-garao City, Manila, Iloilo City, Tacloban, Samal Island, and Davao City. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.
```{r}
tempp <- c(42,39,34,34,30,27)
```
#a. What is the R code and its result for creating a character vector for the city/townof Tuguegarao City, Manila, Iloilo City, Tacloban,Samal Island, and Davao City? Name the object as city. The names should follow the same order as in the instruction.
```{r}
place <- c("Tuguegarao City", "Manila", "Iloilo City", "Tacloban","Samal Island", "Davao City")
```
#b. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.Name the object as temp. Write the R code and its output. Numbers should also follow what is in the instruction.
```{r}
temp <- mean(tempp)
temp
```
#c. Create a dataframe to combine the city and the temp by using ‘data.frame(). Whatthe R code and its result?
```{r}
city_temp <- data.frame(tempp,place)
city_temp
```

#d. Associate the dataframe you have created in 2.(c) by naming the columns using the names() function. Change the column names by using names() function as City andTemperature. What is the R code and its result?
```{r}
names(city_temp) <-  c("Temperature", "City") 
city_temp
```
#e. Print the structure by using str() function. Describe the output.
```{r}



str(city_temp)
```
# It displayed the 2 variable and 6 objects on data frame.

#f. From the answer in d, what is the content of row 3 and row 4 What is its R code and its output?
```{r}



row_content3 <- city_temp[3,]
row_content4 <- city_temp[4,]

row_content3
row_content4

```

#g. From the answer in d, display the city with highest temperature and the city with the lowest temperature. What is its R code and its output?
```{r}



max_index <- max(city_temp$Temperature)
max_index

min_index <- min(city_temp$Temperature)
min_index
```
#2. Create a matrix of one to eight and eleven to fourteen with four columns and three rows.

matrix(c(1,2,3,4,5,6,7,8,9,10,11),nrow=3,ncol=4)

